\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 0\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the Rev 0
Demo.  The time period of interest is the time between the POC demo and the Rev
0 demo.

\section{Demo Plans}

\wss{What will you be demonstrating}

\section{Team Meeting Attendance}

Our team stays in touch regularly through Discord and schedules a
meeting when detailed discussion is needed. Below is the attendance
of all format meetings that have taken place.

\wss{For each team member how many team meetings have they attended over the
  time period of interest.  This number should be determined from the meeting
  issues in the team's repo.  The first entry in the table should be the total
number of team meetings held by the team.}

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Meetings}\\
    \midrule
    Total & 3\\
    Sevhena Walker & 3\\
    Mya Hussain & 3\\
    Ayushi Amin & 3\\
    Nivetha Kuruparan & 3\\
    Tanveer Brar & 3\\
    \bottomrule
  \end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Supervisor/Stakeholder Meeting Attendance}

\wss{For each team member how many supervisor/stakeholder team meetings have
  they attended over the time period of interest.  This number should
  be determined
  from the supervisor meeting issues in the team's repo.  The first entry in the
  table should be the total number of supervisor and team meetings held by the
  team.  If there is no supervisor, there will usually be meetings with
stakeholders (potential users) that can serve a similar purpose.}

We prioritize having in person meetings with our supervisor Dr David
to be able to effectively communicate our progress and concerns. We
have a weekly slot open with the supervisor, but in case there is
little to discuss, the meeting is cancelled for the week and our
progress is communicated via Discord.

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Meetings}\\
    \midrule
    Total & 4\\
    Sevhena Walker & 4\\
    Mya Hussain & 4\\
    Ayushi Amin & 4\\
    Nivetha Kuruparan & 4\\
    Tanveer Brar & 4\\
    \bottomrule
  \end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Lecture Attendance}

We aim to have at least one person attend the lecture so the team is
upto date with all information. In the rare case that no one goes to
the lecture, we update through the lecture slides.

\wss{For each team member how many lectures have they attended over the time
  period of interest.  This number should be determined from the
  lecture issues in
  the team's repo.  The first entry in the table should be the total number of
lectures since the beginning of the term.}

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Lectures}\\
    \midrule
    Total & 2\\
    Sevhena Walker & 1\\
    Mya Hussain & 0\\
    Ayushi Amin & 0\\
    Nivetha Kuruparan & 0\\
    Tanveer Brar & 0\\
    \bottomrule
  \end{tabular}
\end{table}

\wss{If needed, an explanation for the lecture attendance can be provided here.}
\section{TA Document Discussion Attendance}

\wss{For each team member how many of the informal document discussion meetings
with the TA were attended over the time period of interest.}

\begin{table}[H]
  \centering
  \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Lectures}\\
    \midrule
    Total & 2\\
    Sevhena Walker & 2 \\
    Mya Hussain & 2 \\
    Ayushi Amin & 2 \\
    Nivetha Kuruparan & 2 \\
    Tanveer Brar & 2 \\
    \bottomrule
  \end{tabular}
\end{table}

\wss{If needed, an explanation for the attendance can be provided here.}

\section{Commits}

\wss{For each team member how many commits to the main branch have been made
  over the time period of interest.  The total is the total number of
  commits for
  the entire team since the beginning of the term.  The percentage is the
percentage of the total commits made by each team member.}

\begin{table}[H]
  \centering
  \begin{tabular}{lll}
    \toprule
    \textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
    \midrule
    Total & 662 & 100\% \\
    Sevhena Walker & 277 & 41.8429\% \\
    Mya Hussain & 78 & 11.782485\% \\
    Ayushi Amin & 129 & 19.4864\% \\
    Nivetha Kuruparan & 102 & 15.407855\% \\
    Tanveer Brar & 76 & 11.48036\% \\
    \bottomrule
  \end{tabular}
\end{table}

The number of commits does not necessarily reflect the amount of work done by each team member. Some members prefer to make frequent small commits while others make fewer but larger commits that include multiple changes.
Additionally, pair programming sessions often only let one person make the commit so it would only be under their name.

\section{Issue Tracker}

\wss{For each team member how many issues have they authored (including open and
  closed issues (O+C)) and how many have they been assigned (only
    counting closed
issues (C only)) over the time period of interest.}

\begin{table}[H]
  \centering
  \begin{tabular}{lll}
    \toprule
    \textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
    \midrule
    Tanveer Brar & 10 & 67 \\
    Mya Hussain & 18 & 70 \\
    Ayushi Amin & 20 & 79 \\
    Sevhena Walker & 106 & 96 \\
    Nivetha Kuruparan & 35 & 76 \\
    \bottomrule
  \end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{CICD}

\wss{Say how CICD is used in your project}

CI/CD was implemented in the project to automate essential
development and documentation tasks, improving efficiency and
maintaining code quality. The project utilises GitHub Actions
workflows to enforce coding standards, validate changes, and ensure
documentation integrity.

A dedicated workflow formats and compiles \LaTeX{} documents whenever
changes are made to \texttt{.tex} files or their dependencies. This ensures that
only high quality documentation is pushed to the main branch.

Another workflow is responsible for maintaining code consistency and
adhering to best practices. It uses \texttt{ruff} to lint and format
\texttt{.py} files, identifying potential issues such as syntax
errors, unused imports, and style inconsistencies. This workflow
allows the python scripts to be written with a uniform coding style.

The final workflow ensures the correctness of the codebase. It runs
\texttt{pytest} to execute unit and integration tests, validating the
expected behaviour of the software. Additionally, it includes a code
coverage check, ensuring that newly introduced or modified code is
adequately tested. This helps prevent regressions and maintain the
reliability of the project.

\end{document}
